Empirical Research Paper Project

### 2019-12-14 content/assignment/paper-project.Rmd
Add presentation example, class 23 content
Add link to example empirical paper

- [<i class="fas fa-external-link-square-alt"></i> Writing and Reading Empirical Papers Slides](/slides/paper-slides.html)

@@

- **Presentation**: a 5-10 minute presentation of what you have so far. Different people will be at different stages, since your paper is not due yet! Use this as an opportunity to get feedback from me and your classmates, that might help you finish your project. Using some slides to show tables, models, and plots is highly recommended.

>>>>

- [<i class="fas fa-external-link-square-alt"></i> Writing and Reading Empirical Papers Slides](/slides/paper-slides.html)
- [<i class="fas fa-github"></i> Example Paper Project](https://github.com/ryansafner/example_empirical_paper)

@@

- **Presentation**: a 5-10 minute presentation of what you have so far. Different people will be at different stages, since your paper is not due yet! Use this as an opportunity to get feedback from me and your classmates, that might help you finish your project. Using some slides to show tables, models, and plots is highly recommended.
  - [<i class="fas fa-file-pdf"></i> Example](/papers/Presentation_example.pdf)
